---
title: "Alcohol vs Seat choice"
author: "Taylor Stohl"
date: "Summer 2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r include=FALSE}
require(tidyverse)
require(tigerstats)
davisdata <- read.csv(file="UCDavis.csv")
```
Our Goal is to answer this question Is there a difference between the alcohol consumed between the row
you choose to sit in??

## Now with ggplot - first select the basic data

```{r}
basicCN <- ggplot(davisdata,aes(y=alcohol,x=Seat))
```
## Now add in boxplot

```{r}
basicCN + geom_boxplot()
```
  
  
### get fancy  

```{r}
basicCN + geom_boxplot(notch=TRUE,outlier.color = "red") + stat_boxplot(geom ='errorbar') + labs(title="Fancy notch boxplot \n with 2 lines")
```

This boxplot shows  that those who sit in the back drink substantially more than those who sit in the middle and front. Over 75% of people who sit in the back drink more than anyone sitting in the middle and front.




## Numerical Summarys 

```{r}
favstats(alcohol~Seat,data=davisdata)
```

It appears that students sitting in the back of the class consumed a mean of 9.625 ounces of alcohol a week. Furthermore, people who sit in the back of the class, drink about three times more alcohol than people who sit in the middle and the front of the class. 

## Inferential Tests

```{r}
model1 <- aov(alcohol~Seat,data=davisdata)
summary.aov(model1)
```
The P-value is so small (0.000116), that it is unlikely the alcohol consumption is the same in all 3 seat positions. The null hypothesis is rejected; they do not drink the same amount.



## When significant follow up with TukeyHSD  

```{r}
plot(TukeyHSD(model1))
```


This TukeyHDS plot shows that those who sit in the back drink significantly more than those in the front.
This plot also shows that those in the back seats drink a much larger quantity of alcohol than those seated in the middle. However, it shows no difference in alcohol consumption between the middle and the front.
If zero is in the confidence interval that means there is no difference.
(The confidence interval is the dotted line above zero.)




## Conclusions

There is a difference in alcohol consumption and seat position. Those who sit in back drink approximately three times more than those who sit in the middle and front. There isn't a difference in consumption of alcohol between the middle and front.

